Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
         scale_x_continuous(breaks = brs,
	   labels = insert_minor(brs, 5, start = century(min(df2$publication_decade)))) + 
         scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10)

@@

```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=11}
df <- df.full %>% filter(publication_year >= 1640 &
                         publication_year <= 1911) %>%
              group_by(catalog, publication_year) %>%
              summarize(title_length = median(title_length_wordcount),
	      		n = n())

pics <- list()
brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
for (catal in unique(df$catalog)) {
  pics[[catal]] <- ggplot(subset(df, catalog == catal),
       aes(x = publication_year, y = title_length)) +
       geom_point(aes(size = n)) +
       geom_smooth(color = "black") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(limits = c(0, max(na.omit(df$title_length)))) +
       ggtitle(paste("Mean title length (", catal, ")", sep = "")) + 
       xlab("Publication year") +
       ylab("Title length (words)")
}

library(gridExtra)
grid.arrange(pics[[1]], pics[[2]], nrow = 1)
```

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +
       scale_fill_stata() +       
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 1)) +   
       ggtitle(paste("Publishers (", catal, ")", sep = ""))

@@

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 1)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +
       scale_fill_stata() +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = min(npub$publication_decade))) + 
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle(paste("Publishers (", catal, ")", sep = ""))

@@

brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 1)

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Publication decade") +
       ylab("Title count (n)") +
       ggtitle("Title count (absolute)") +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) +                           
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

df1 <- df1 %>% summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
	         mean_title_length = mean(title_length_wordcount, na.rm = TRUE))

@@

@@

```{r Fig19, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, fig.show="hold"}
sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
catalogue <- "Fennica"

@@

# PAPER CONSUMPTION
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
       geom_line(aes(color = language)) +       
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
       scale_color_stata() +
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       
       scale_y_continuous(label = scientific_10) + 
       ggtitle(paste("Devotional literature (", catalogue, ")", sep = ""))

>>>>

  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
         scale_x_continuous(breaks = brs,
	   labels = insert_minor(brs, 5, start = 1500)) + 
         scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10)

@@

```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=12}
df <- df.full %>% filter(publication_year >= 1640 &
                         publication_year <= 1911) %>%
              group_by(catalog, publication_year) %>%
              summarize(title_length = median(title_length_wordcount),
	      		n = n())

pics <- list()
brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
brsy <- seq(0, round(max(na.omit(df$title_length)), -1), 10)
for (catal in unique(df$catalog)) {
  pics[[catal]] <- ggplot(subset(df, catalog == catal),
       aes(x = publication_year, y = title_length)) +
       geom_point(aes(size = n)) +
       geom_smooth(color = "black") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2), limits = c(0, max(na.omit(df$title_length)))) +
       ggtitle(paste("Average title length (", catal, ")", sep = "")) + 
       xlab("Publication year") +
       ylab("Title length (words)")
}

#library(gridExtra)
#grid.arrange(pics[[1]], pics[[2]], nrow = 1)

library(cowplot)
# arrange the three plots in a single row
prow <- plot_grid(
           pics[[1]] + theme(legend.position="none"),
           pics[[2]] + theme(legend.position="none"),
           align = 'vh',
           labels = c("A", "B"),
           hjust = -1,
           nrow = 1
           )

# extract the legend from one of the plots
# (clearly the whole thing only makes sense if all plots
# have the same legend, so we can arbitrarily pick one.)
legend_b <- get_legend(pics[[1]] + theme(legend.position="right"))

# add the legend underneath the row we made earlier. Give it 10% of the height
# of one plot (via rel_heights).
p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
print(p)
```

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +
       scale_fill_stata() +       
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +   
       ggtitle(paste("Publishers (", catal, ")", sep = ""))

@@

npub <- unique(df) %>% group_by(publication_decade, publication_place) %>% tally()
npub$publication_place <- factor(npub$publication_place, levels = top)
npub.kungliga <- npub
npub <- bind_rows(npub.fennica, npub.kungliga)

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Publishers (n)") +
       scale_fill_stata() +
       scale_x_continuous(breaks = brs,
           labels = insert_minor(brs, 5, start = min(npub$publication_decade))) + 
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle(paste("Publishers (", catal, ")", sep = ""))

@@

brs <- seq(min(df$publication_year), max(df$publication_year), 1)

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
brsy <- seq(0, max(df$n), 1e3)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Publication decade") +
       ylab("Title count (n)") +
       ggtitle("Title count (absolute)") +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2)) +                                  
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

df1 <- df1 %>%
	       group_by(publication_decade, publication_place) %>% 
  	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
	         mean_title_length = mean(title_length_wordcount, na.rm = TRUE))

@@

df <- bind_rows(df1, df2)
df$publication_place <- factor(df$publication_place)

@@

```{r Fig19, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat")
catalogue <- "Fennica"

@@

# PAPER CONSUMPTION
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
       geom_line(aes(color = language), size = 1) +       
       xlab("Year") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
       scale_color_stata() +
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       
       scale_y_continuous(label = scientific_10) + 
       ggtitle(paste("Devotional literature (", catalogue, ")", sep = ""))
